\chapter{Shortcomings}
\ifpdf
    \graphicspath{{Chapter2/Chapter2Figs/PNG/}{Chapter2/Chapter2Figs/PDF/}{Chapter2/Chapter2Figs/}}
\else
    \graphicspath{{Chapter2/Chapter2Figs/EPS/}{Chapter2/Chapter2Figs/}}
\fi

In spite of all efforts some negative aspects will always remain. Here are a few negative points associated with Synergy Sansthan.

\section{Low awareness}
% \markboth{\MakeUppercase{\thechapter. My Second Chapter }}
One problem that I felt with Synergy Sansthan was that it was not able to spread awareness in Harda city itself. The place where its office was located, neighborhood people didn't know much about it. They did not know much about the activities or some people didn't even know that it existed.

\section{Employees}
% \markboth{\MakeUppercase{\thechapter. My Second Chapter }}
At Synergy Sansthan some of the employees worked with a lot of enthusiasm as they actually wanted to help the society and do good whereas there were some who just worked there like a normal job. They did not take much interest in and only did what they were told. They did not take any initiatives on their own or do some work which was slightly out of the way. Due to this, there was some negligence in the NGO as well. 

In December 2013, the child line team rescued 2 girls from the railway station from a trafficking racket. Those 2 girls were kept over night at the office under the supervision of 2 female employees of the NGO. In the morning the employees left the office to get some refreshments and the 2 rescued girls escaped the office. Then the NGO had to search neighboring villages for the girls. It was only after 11 days that they were found again. Such negligence should not take place when the pertaining matter is so sensitive. 

\section{Low funds}
Synergy Sansthan as an organization is not able to monitor large amount of donations single handedly. Most of its source of funding is from bigger NGOs and through Government programs. It is not able to secure large donations from individuals. This restricts the activities that it can organize and the extent as well.

% \subsection{first subsection in the Second Section}
% ... and some more ...

% \subsection{second subsection in the Second Section}
% ... and some more ...

% \subsection{third subsection in the Second Section}
% ... and some more ...


% ------------------------------------------------------------------------

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
